animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-28 animbook-journal.Rmd
small fixes

# Introduction

@@

The structure of this paper is as follows. The section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools, and how they are employed for this problem. A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

# Explanation of the New York Times visualization {#NYT}

@@

# Data

@@

```{r data-diagram, fig.cap="The diagram shows what are the expected data forms.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
knitr::include_graphics("figures/data-diagram.png")
```

@@

# Animation tools

@@

# Visualization design

@@

# Software

@@

## Overviw of functions

>>>>

# Introduction {#intro}

@@

The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools, and how they are employed for this problem. A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

# Explanation of the New York Times visualization {#NYTvis}

@@

# Data {#data}

@@

```{r data-diagram, fig.cap="The data can be provided in the raw or categorized form, and will be processed into the format needed for the animation.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page"}
knitr::include_graphics("figures/data-diagram.png")
```

@@

# Animation tools {#animation}

@@

# Visualization design {#design}

@@

# Software {#software}

@@

## Overview of functions
